PANCHANGE_data_preprocessing

### 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd
adding headers with #

Psychotic disorders group
[63] "mhd.schizophrenia_numeric"                                 
[64] "mhd.schizoaffective_disorder_numeric"                      
[65] "mhd.type_psychosis_psychotic_illness_numeric" 
```{r mhd psychotic_disorders}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    psychotic_disorders_numeric =
      case_when(
        mhd.schizophrenia_numeric == "1" ~ 1,
        mhd.schizoaffective_disorder_numeric == "1" ~ 1,
        mhd.type_psychosis_psychotic_illness_numeric == "1" ~ 1,
        (mhd.schizophrenia_numeric == "0" &
        (mhd.schizoaffective_disorder_numeric == "0" | is.na(mhd.schizoaffective_disorder_numeric == "0") & #NA included because some cohorts don't have schizoaffective disorder
        mhd.type_psychosis_psychotic_illness_numeric == "0") ~ 0)
        )
    )

>>>>

### Psychotic disorders
"mhd.schizophrenia_numeric"                                 
"mhd.schizoaffective_disorder_numeric"                      
"mhd.type_psychosis_psychotic_illness_numeric" 
```{r mhd psychotic_disorders}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    psychotic_disorders_numeric =
      case_when(
        mhd.schizophrenia_numeric == "1" ~ 1,
        mhd.schizoaffective_disorder_numeric == "1" ~ 1,
        mhd.type_psychosis_psychotic_illness_numeric == "1" ~ 1,
        (mhd.schizophrenia_numeric == "0" &
        (mhd.schizoaffective_disorder_numeric == "0" | is.na(mhd.schizoaffective_disorder_numeric == "0") & #NA included because some cohorts don't have schizoaffective disorder
        mhd.type_psychosis_psychotic_illness_numeric == "0") ~ 0)
        )
    )
